\begin{thebibliography}{12}
 \addcontentsline{toc}{chapter}{Bibliografia}
 
\bibitem{bernard05}
	Bernard A.B. [2005], 
	\emph{An Index of Oscar-Worthiness: Predicting the Academy Award for Best Picture}, Hanover.
\bibitem{chen10}
	Chen X. i in. [2010], 
	\emph{Logistic Regression with Stata}, \url{http://www.ats.ucla.edu/stat/stata/webbooks/logistic/}, dostęp: czerwiec 2013, rozdz. 1-3.
\bibitem{helmer13}
	Helmer E. [2013],
	\emph{The Value of an Oscar}, \url{http://boxofficequant.com/the-value-of-an-oscar/}, Reuters, dostęp: czerwiec 2013.	
\bibitem{kaplan06}
	Kaplan D. [2006], 
	\emph{And the Oscar Goes to…A Logistic Regression Model for Predicting Academy Award Results}, Journal Of Applied Economics and Policy, XXV, s.23-41.
\bibitem{krauss08}
	Krauss J. i in. [2008], 
	\emph{Predicting movie success and acadamy awards through sentiment and social network analysis}, Koeln.
\bibitem{mycielski10}
	Mycielski J. [2010], 
	\emph{Ekonometria}, Warszawa.
\bibitem{nelson01}
	Nelson R. A. i in. [2001], 
	\emph{What's an Oscar Worth?}, Economic Inquiry, 39(1).
\bibitem{pardoe08}
 	Pardoe I., Simonton D.K. [2008], 
  	\emph{Applying discrete choice models to predict Academy Award winners}, 
  	The Journal of the Royal Statistical Society, Series A, s.375-394.
 \bibitem{pardoe08}
 	Pardoe I. [2012], 
 	\emph{Applied Regression Modeling}, Oregon, rozdz.7.2.
 \bibitem{royston99}
	Royston P., Ambler G. [1999],
	\emph{Nonlinear regression models involving power or exponential functions of covariates},
	Stata Technical Bulletin 49, s.25-30.
\bibitem{simonton05}
	Simonton D. K. [2005],
	\emph{Cinematic creativity and production budgets: does money make the movie?},
	Journal of Creative Behavior, nr 39, s.1-15.
 	
 	
 \end{thebibliography}